\documentclass[a4paper,10pt]{article}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{pythontex}

\titleformat{\section}{\large\bfseries}{\thesection}{{1em}}{{}}[{{\titlerule[0.8pt]}}]

\begin{document}

\pagestyle{empty}

\begin{center}
    \textbf{\LARGE {John} {Doe}} \\
    {jd@gmail.com} | {123-456-7890} | LinkedIn: {linkedin.com/in/johndoe}
\end{center}

\section*{Objective}
{
Experienced Mechanical Eng.}

\section*{Professional Experience}
{ in this.
\textbf{Software Engineer - Tech Solutions Inc., City, Country - 2019-Present}

\begin{itemize}
    \item Developed and maintained web applications using Python, Django, and JavaScript, delivering feature-rich and responsive user interfaces.
    \item Led the implementation of a modular and scalable e-commerce platform, resulting in a 20\% increase in sales.
    \item Conducted code reviews, provided mentorship to junior developers, and actively participated in continuous improvement initiatives.
\end{itemize}

\textbf{Intern, Software Development - ABC Tech, City, Country - 2017-2019}

\begin{itemize}
    \item Contributed to the design and development of new software features, demonstrating proficiency in Java, JavaScript, and SQL.
    \item Assisted in the implementation of a data analytics tool, enabling the team to gain valuable insights into user behavior.
\end{itemize}

\textbf{IT Support Specialist - XYZ Company, City, Country - 2016-2017}

\begin{itemize}
    \item Provided technical support to end-users, diagnosing and resolving hardware and software issues in a timely manner.
    \item Implemented system upgrades and maintenance procedures, ensuring optimal performance of computer systems.
\end{itemize}}

\section*{Skills}
\begin{flushleft}
{

\textbf{Programming Languages:} Python, C++, JavaScript \\
\textbf{Frameworks/Libraries:} Django \\
\textbf{Databases:} MySQL, PostgreSQL \\
\textbf{Cloud Services:} AWS \\
\textbf{Version Control:} Git \\
\textbf{DevOps:} Docker, Jenkins, Puppet, Chef, Terraform}
\end{flushleft}

\section*{Education}
{2015 - 2019 Bachelor of Science in Computer Science, University of XYZ, City, Country}

\section*{Certifications}
{

Certified Python Developer, XYZ Certification}

\end{document}