\documentclass[11pt, a4paper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.9]{geometry}

\name{John}{Doe}
\email{jd@gmail.com}
\phone{123-456-7890}
\social[linkedin.com/in/johndoe]{linkedin.com/in/johndoe}

\begin{document}

\makecvtitle

\section{Professional Summary}
{

Dedicated and dynamic software engineer with a proven track record of delivering innovative and impactful solutions. Highly skilled in full-stack web development, particularly proficient in Python and Django. Strong ability to collaborate effectively within cross-functional teams and a passion for tackling complex challenges. Focused on designing scalable solutions to drive business success.}

\section{Education}
\cventry{}{2015 - 2019 Bachelor of Science in Computer Science, University of XYZ, City, Country}{}{}{}{}

\section{Work Experience}
\cventry{}{
\textbf{Software Engineer, Tech Solutions Inc., City, Country} \hfill 2019-Present
\begin{itemize}
  \item Develop and maintain web applications using Python, Django, and JavaScript, delivering feature-rich and responsive user interfaces.
  \item Lead the implementation of a modular and scalable e-commerce platform, resulting in a 20\% increase in site performance.
  \item Conduct code reviews, provide mentorship to junior developers, and actively participate in continuous improvement initiatives.
\end{itemize}
\textbf{Intern, Software Development, ABC Tech, City, Country} \hfill 2017-2019
\begin{itemize}
  \item Contribute to the design and development of new software features, demonstrating proficiency in Java, JavaScript, and SQL.
  \item Assist in the implementation of a data analytics tool, enabling the team to gain valuable insights into user behavior.
\end{itemize}
\textbf{IT Support Specialist, XYZ Company, City, Country} \hfill 2016-2017
\begin{itemize}
  \item Provide technical support to end-users, diagnosing and resolving hardware and software issues in a timely manner.
  \item Implement system upgrades and maintenance procedures, ensuring optimal performance of computer systems.
\end{itemize}
\vspace{5pt}}{}{}{}{}

\section{Skills}
\cvitem{}{
Programming: Python, JavaScript, Java
Web Frameworks: Django, React
Database: MySQL, PostgreSQL
Version Control: Git
Tools: Docker, Jenkins
Soft Skills: Team Collaboration, Problem Solving, Communication}

\section{Projects}
\cvitem{}{, just follow these rules and provide the result
\textbf{E-commerce Platform, Tech Solutions Inc., City, Country}
\begin{itemize}
    \item Led the development of a scalable and modular e-commerce platform using Python, Django, and React.
    \item Implemented secure payment gateways, product recommendation algorithms, and enhanced user authentication mechanisms.
\end{itemize}
\noindent\textbf{Project Title, Company/Client, City, Country}
\begin{itemize}
    \item Developed a data management system using SQL and MongoDB for a client in the retail industry.
    \item Designed and implemented an automated testing framework using Selenium and Cucumber for a software company.
\end{itemize}
\noindent\textbf{Project Title, Company/Client, City, Country}
\begin{itemize}
    \item Prototyped and designed a mobile application for a non-profit organization using React Native and Firebase.
    \item Established efficient deployment processes using Docker and Kubernetes for a startup company.
\end{itemize}}

\section{Certifications}
\cvitem{}{
Certifications: 
- Certified Python Developer, XYZ Certification}

\end{document}