\documentclass[11pt, a4paper, sans]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.9]{geometry}

\name{John}{Doe}
\phone{123-456-7890}
\email{johndoe@example.com}
\social[linkedin]{linkedin.com/in/johndoe}

\begin{document}
\makecvtitle

\section{Professional Summary}\label{professional-summary-1}
Results-driven and highly skilled software engineer with a passion for creating efficient and scalable solutions. Proven expertise in full-stack web development using Python and Django. Strong collaborator with a keen ability to solve complex problems.

\section{Education}\label{education}
\cventry{}{Bachelor of Science in Computer Science}{University of XYZ}{City, Country}{}{}

\section{Work Experience}\label{work-experience}
\cventry{}{Software Engineer, Present}{Tech Solutions Inc.}{City, Country}{}{
\begin{itemize}
    \item Developed and maintained web applications using Python, Django, and JavaScript.
    \item Collaborated with cross-functional teams to deliver feature-rich and responsive user interfaces.
    \item Led the implementation of a modular and scalable e-commerce platform, resulting in a 20\% increase in efficiency.
\end{itemize}
}

\cventry{}{Intern, Software Development, 2019-2020}{ABC Tech}{City, Country}{}{
\begin{itemize}
    \item Contributed to the design and development of new software features using Java and JavaScript.
    \item Assisted in the implementation of a data analytics tool, providing valuable insights into user behavior.
\end{itemize}
}

\cventry{}{IT Support Specialist, 2018--2019}{XYZ Company}{City, Country}{}{
\begin{itemize}
    \item Provided technical support to end-users, diagnosing and resolving hardware and software issues.
    \item Implemented system upgrades and maintenance procedures for optimal performance.
\end{itemize}
}

\section{Skills}\label{skills}
\cvitem{}{Python, Django, JavaScript, Java, Git, Docker}

\section{Projects}\label{projects}
\cvitem{}{E-commerce Platform: Led the development of a scalable and modular e-commerce platform using Python, Django, and React. Implemented secure payment gateways, product recommendation algorithms, and enhanced user authentication mechanisms.}

\section{Certifications}\label{projects-1}
\cvitem{}{Certified Python Developer (XYZ Certification)}

\end{document}